

\begin{abstract}
    This will be the document where I write everything I know about what I learn during my studies.
    I hope it serves me in the future as a "go to" document when I need to remind something.
\end{abstract}

\section*{\hfil Introduction \hfil}\label{sec:intro}
\par This document will focus on definitions, understanding concepts and transmitting intuitions/perspectives. 
\par Each chapter will have the same structure. First the definitions and logic connections between everything with references to derivations and demonstrations that will be in attach at the end of the document. Second an overview of the derivations and how formula connect together to make a quick \& easy way of finding the connections for hurry times.
And third, simply one or two pages with the most important formulas from that chapter.
\par The first chapter will be about antennas. The second about microwaves. And the ones after that will consist of applications such as Microwave Links/ Hertzian Beams, Satellites and Radar. Maybe I'll join in a chapter about Probabilistic/Statistic Detection and Estimation of signals and one about some fundamentals of communications.
\par Please be aware that this is a document always at work. I'll write right here when I think a certain chapter is closed, otherwise it might be target of modifications.

\par Finally, there's a resource folder that I'll be refferencing frequently. It has many of my notes hand written, books, slides. Things I thought to be interesting or important. Probably all books mentioned in any section will be there. 
\begin{center}
    \par This folder can be accessed through my \href{https://drive.google.com/drive/folders/1lhU0XlDLMHOkMt60VkjH9rhP8QEZuinX?usp=sharing}{\ul{Shared Drive Link}}    
\end{center}


\vspace{1cm}
\begin{center}
    Enjoy
\end{center}




%attention, only figures and tables with captions will appear!
%\listoffigures

%\listoftables